%%
%% This is file `sample-vem.tex',
%% which is a modified version of `sample-sigconf.tex'.
%%
\documentclass[sigconf]{acmart} % The `anonymous' option is for double-blind review process.

\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

\usepackage{mdframed}

\usepackage{listings}

\lstset{
  basicstyle=\ttfamily\small,
  keywordstyle=\color{blue},
  commentstyle=\color{gray},
  stringstyle=\color{green!50!black},
  showstringspaces=false,
  numbers=none,
  numberstyle=\tiny,
  breaklines=true,
  frame=single
}

\mdfsetup{skipabove=\topskip,skipbelow=\topskip}
\mdfdefinestyle{poistyle}{%
    frametitlerule=true,
}
\mdtheorem[style=poistyle]{poi}{Improvement}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}


%% These commands are for a PROCEEDINGS abstract or paper.
% \acmConference[SBES'24]{Brazilian Symposium on Software Engineering}{September 30 -- October 04,  2024}{Curitiba, PR}

%%
%% end of the preamble, start of the body of the document source.


\settopmatter{printacmref=false} % This command was added for submissions to VEM
\setcopyright{none} % This command was added for submissions to VEM
\renewcommand\footnotetextcopyrightpermission[1]{} % This command was added for submissions to VEM

\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Kworkflow: a Linux kernel Developer Automation Workflow System}
%enviar email para os chairs para atualizarmos o título
\pagestyle{empty}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.
\author{David Tadokoro}
\email{davidbtadokoro@usp.br}
\orcid{}
\affiliation{%
    \institution{University of São Paulo}
  % \institution{Universidade de São Paulo}
  % \state{São Paulo}
  \country{Brazil}
}

\author{Rodrigo Siqueira}
\email{siqueirajordao@riseup.net}
\orcid{}
\affiliation{%
    \institution{University of São Paulo}
  % \institution{Universidade de São Paulo}
  % \state{São Paulo}
  \country{Brazil}
}

\author{Paulo Meirelles}
\email{paulormm@ime.usp.br}
\orcid{0000-0002-8923-2814}
\affiliation{%
    \institution{University of São Paulo}
  % \institution{Universidade de São Paulo}
  % \state{São Paulo}
  \country{Brazil}
}




%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Pilone et al.}

\begin{abstract}
  The Linux kernel is a central project to the Free/Libre and Open Source
  Software (FLOSS) ecosystem. Developers who interact with the kernel source
  code routinely face a variety of repetitive and error-prone tasks, including
  setting up testing environments, managing kernel configuration files,
  compiling with various toolchains, deploying to varied targets, and correctly
  submitting patches. These tasks, though essential, often require handcrafted
  scripts that become fragile, difficult to maintain, and disconnected from the
  core development goals. Kworkflow (kw) is a Developer Automation Workflow
  System (DAWS) that aims to provide high-quality tools that mitigate known
  bottlenecks experienced by kernel developers in their daily workflows. It
  provides a unified Command-Line Interface (CLI) that automates and streamlines
  many tasks, allowing practitioners to focus more on developing code and less
  on setup overhead and details. The hub-like design of the project reflects its
  philosophy of incorporating existing tools to avoid duplication of efforts and
  wasted resources from the community, a by-product of the many \textit{ad-hoc}
  scripts developers commonly produce. The kw tool also offers a data collection
  infrastructure, which makes it an excellent platform for further scientific
  research in the Linux kernel development model. In this sense, kw serves as a
  robust tool for real kernel developers and an opportunity for academic
  research work.
\textbf{\href{https://archive.softwareheritage.org/swh:1:cnt:3695bf04c525dc03d850baa96485d7bcdca7f9b3;origin=https://github.com/davidbtadokoro/sbes-tool-2025-kw-demo;visit=swh:1:snp:21a2e8110b4a8c659c6ba451723f836d9fbba8db;anchor=swh:1:rev:1cef3fedffb5a4848bfe8f337cf1acd1380a7793;path=/sbes-tool-2025-kw-demo.mp4}{Link to the Kworkflow demo video}}~\cite{kw-demo-video}.
\end{abstract}


%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Linux, Free Software, Linux kernel development model, Free Software development model, software engineering, kernel workflows.}

% \received{2 June 2024}
% \received[revised]{12 March 2009}
% \received[accepted]{5 June 2009}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\input{sections/intro}
\input{sections/background}
\input{sections/kw}
\input{sections/conclusion}

\section*{Artifacts Availability}

\begin{itemize}
  \item kw official repository: \url{https://github.com/kworkflow/kworkflow}
  \item kw Software Heritage archive: \url{https://archive.softwareheritage.org/browse/origin/directory/?origin_url=https://github.com/kworkflow/kworkflow}
  \item kw website: \url{https://kworkflow.org}

\end{itemize}

\begin{acks}
  This study was financed, in part, by CAPES (Finance Code 001), the University of São Paulo – USP (Proc. 22.1.9345.1.2), the São Paulo Research Foundation – FAPESP (Proc. 19/26702-8) and the São Paulo State Data Analysis System Foundation – SEADE (Proc. 2023/18026-8), Brazil. We also thank the community for collaboratively building and maintaining kw, members of the Linux ecosystem for the feedback provided, and the students from IME-USP who have voluntarily fostered the project throughout the years.
\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
\endinput
